\Huge Visualization Interactivity Perception Research \\ on Data Journalism

### 2017-05-01 paper/main.tex
final v1

Through this practical experiment, we dedicate to explore the relationship between user perception and interactive, four hypotheses are proposed in our study, which is listed in Section 3.

@@

\section{Experiment}
\large
\begin{table}
	\centering
		\begin{tabular}{|c|c|c|c|}
		\hline
     	&Level 0&Level 1&Level 2\\
     	\hline
            		&Static diagram&Drag & Level 2 plus\\ 
        Interactive& with tool tips&Multiple Charts& instruction\\
					&             &   			&Sort Buttons\\
     	\hline
        \end{tabular}
     \caption{Three level of Interactive}
\end{table}
\subsection{Hypotheses}
Based on the related work, we decide to divide the interactivity perception experiment into three levels. The hypothesis we put forward are listed as follows.\\
\textbf{Hypothesis 1.} Users are easier to perceive the information with higher interaction.\\
\textbf{Hypothesis 2.} Users are more willing to engage in the story with higher interaction.\\
\textbf{Hypothesis 3.} Higher level of interactive visualization can improve user's perception for data journalism.\\
\textbf{Hypothesis 4.} Higher level of interactive visualization can reduce the misleading by article.\\

@@

We took a step out to evaluate if the different level of interactive can affect the audience of the newspapers online in data journalism. For the experiment itself, we used five kinds of the common interactive methods, as the front-end technology fast changing, the future research should consider not only the classic methods but the latest visualization technology. Meanwhile, with the time limitation, we can not find a more random sample to join this experiment, it should be improved in the future work.

In the next stage, we decided to make a crowd-source experiment and collect more different kinds of data-driven news like entertainment and sport to balance the bias of the different audience reading preference, to make the result more convincing.

In the time spending part, the significant higher time spending for high interaction, which might cause by the complexity. In the next stage, we can add a new group of participants that was introduced how to use these visualizations first. Measure the time spending, and accuracy/skip rate of this group might bring more insights. What's more, a more careful design of interaction need to be considered since the accuracy rate of Level 2, and Level 1 didn't outperform Level 1, which might be caused by lacking the learning stage for interaction.

@@

In this paper, we did a 3-Level experiment to measure the influence of the different degree of data interactive to the data news in the data journalism.  Level 0 for the original article, Level 1 for the visualization with light Interactive, Level 2 for the bi-directional visual interaction. In the experiment, the 3-Level visualization all bounded on the same article. Then we evaluated the visitor stay time data to analysis the effect of interactive of the different level.

The result showed that users are more likely to engage in the interactivity. Users can perceive the information faster than no interactivity while a complex interactivity might make users confused and cause a misleading result.

>>>>

Through this practical experiment, we dedicate to explore the relationship between user perception and interactive, three hypotheses are proposed in our study, which is listed in Section 3.

@@

\section{Experiment}
\large
\begin{table}
	\centering
		\begin{tabular}{|c|c|c|c|}
		\hline
     	&Level 0&Level 1&Level 2\\
     	\hline
            		&Static diagram&Drag & Level 2 plus\\ 
        Interactive& with tool tips&Multiple Charts& instruction\\
					&             &   			&Sort Buttons\\
     	\hline
        \end{tabular}
     \caption{Three level of Interactive}
\end{table}
\subsection{Hypotheses}
Based on the related work, we decide to divide the interactivity perception experiment into three levels. The hypothesis we put forward are listed as follows.\\
\textbf{Hypothesis 1.} Users are easier to perceive the information with higher interaction.\\
\textbf{Hypothesis 2.} Users are more willing to engage in the story with higher interaction.\\
\textbf{Hypothesis 4.} Higher level of interactive visualization can reduce the misleading by article.\\

@@

We took a step out to evaluate if the different level of interactive can affect the audience of the newspapers online in data journalism. For the experiment itself, we used five kinds of the common interactive methods, as the front-end technology fast changing, the future research should consider not only the classic methods but the latest visualization technology. Meanwhile, with the time limitation, we can not find a more random sample to join this experiment, it should be improved in the future work. The null hypothesis as well as the test of significance can be included in the future research.

On the next stage, we decided to make a crowd-source experiment and collect more different kinds of data-driven news like entertainment and sport to balance the bias of the different audience reading preference, to make the result more convincing.

In the time spending part, the higher interactions will prominently leads to  more time spending, which might cause by the complexity. In the next stage, we can add a new group of participants that was introduced how to use these visualizations first. Measure the time spending, and accuracy/skip rate of this group might bring more insights. What's more, a more careful design of interaction need to be considered since the accuracy rate of Level 2, and Level 1 didn't outperform Level 1, which might be caused by lacking the learning stage for interaction.

@@

In this paper, we did a 3-Level experiment to measure the influence of the different degree of data interactive to the data news in the data journalism.  Level 0 for the original article, Level 1 for the visualization with light Interactive, Level 2 for the bi-directional visual interaction. In this experiment, the 3-Level visualization all bounded on the same article. Then we evaluated the visitor stay time data to analysis the effect of interactive of the different level.

In conclusion, our study provide further insights on the relation between user preference and visualization interactions in data journalism, the results show that users are more likely to engage in the interactivity. Users can perceive the information faster than no interactivity while a complex interactivity might make users confused and cause a misleading result. However, the higher interactive visualization in our case can actually reduce the misleading rate by ambiguous context. Furthermore, moderately reduce the space of context can also increase users willing in participating visualization interactions.  Further analytic and statistical investigations are needed to address issues on the mechanism behind the different interactive technology and user behavior.
